---
title: "Protective Hypothermia Part 4"
author: "Anthony Morada and Garrison Davis"
date: "February 25, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
# Working with cleaned and deidentified data. Saved within this repository.
df <- read.csv("./prot-hypothermia.csv")

require(ggplot2)
knitr::opts_chunk$set(fig.width=10, fig.height=6) 

```


## Original Data

First 6 lines of deidentified data:
```{r original data present, echo=F}
head(df)
dt <- df[is.na(df$Temp) == F & is.na(df$VIS) == F,]
```

Data contains `r nrow(df)` time points.There are `r length(levels(df$Name))` unique patients in this report. There are `r summary(df$Name)` time points for `r levels(df$Name)` respectively.

  
However, not all of the rows contain Temperature or VIS Scores. Out of the `r nrow(df)` time points in this data table, `r nrow(df[is.na(df$Temp) == F & is.na(df$VIS) == F,])` contained both VIS and Temperature Values. Rows without Temperature or VIS values were removed. After subset, `r summary(dt$Name)` time points were found for patients `r levels(dt$Name)` respectively. Unfortunately after subset, pt#8 only had 1 eligible row and had to be removed from the analysis leaving 

```{r, echo=F}
dt <- dt[dt$Name != "pt#8",]
dt$Name <- factor(dt$Name)
rm(df)
```

Therefore, the final table before analysis contains `r length(levels(dt$Name))` patients with `r nrow(dt)` time points that have both VIS and Temperature values. Patients  `r levels(dt$Name)` have `r summary(dt$Name)` time points respectively. 

```{r plot, echo=FALSE}

ggplot(data=dt, aes(x = Hour, y = Temp, color = Name)) + 
     geom_line() +
     labs(x= "Hour", y= "Temperature (C)", title = "Temperature Over Time")

ggplot(data=dt, aes(x = Hour, y = VIS, color = Name)) + 
     geom_line() +
     labs(x= "Hour", y= "VIS", title = "VIS Over Time")

ggplot(data=dt, aes(x = Temp, y = VIS, color = Name)) + 
     geom_point() +
     geom_smooth(method = "lm", se = FALSE) +
     geom_text(aes(label = Hour), position = position_nudge(y = -200)) +
     labs(x= "Temperature (C)", y= "VIS", title = "Hypothermia VIS Score")
```





